Cybersecurity Is Too Important\\To Be Left To The Specialists

### 2019-03-14 FIE2019.tex
JHD added his ToDo
Added a GDPR paragraph plus couple of typos

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{paralist}
\usepackage{url}
\usepackage{enumitem}
\usepackage[hyphenbreaks]{breakurl}
\usepackage[T1]{fontenc}
\usepackage{booktabs} % For formal tables

@@

The Payments Industy \cite[6.6]{PCI2018b} insists on either independent code reviews by security specialists or a Web Application Firewall: essentially saying that the normal development process even after developers are trained in secore coding practices \cite[6.5]{PCI2018b} cannot be trusted to deliver secure code.

>>>>

% JHD to
% a) Add the Bonn work
% b) Add ABET stuff and ask Tom P to cross-check.
\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{paralist}
\usepackage{url}
\usepackage{enumitem}
\usepackage[hyphenbreaks]{breakurl}
\usepackage[T1]{fontenc}
\usepackage{booktabs} % For formal tables

@@

In particular the expectation of ''Privacy by Design'' and and by "Privacy by Default" has significant implications for all software development with a European context that processes personal data. Whilst both ''Privacy by Design'' and ''Privacy by Default' have been expected good practices for a number of years they expectations now have a legal dimension. A number of studies have documented the challenges of aligning security methods in Agile Practices \cite{vanderHeijden:2018:EPS:3239235.3267426}. This further emphasizes the need for mainstream software developers and by extension Computer Science graduates to be versed in relevant security practices.

The Payments Industry \cite[6.6]{PCI2018b} insists on either independent code reviews by security specialists or a Web Application Firewall: essentially saying that the normal development process even after developers are trained in secure coding practices \cite[6.5]{PCI2018b} cannot be trusted to deliver secure code.
